---
title: "Geunchul Shin's personal website"
---

Welcome to my website!

My name is Geunchul Shin, currently attending University of Toronto majoring in African Studies and minoring in mathematics and statistics. It is a mix that shows my love for cultural insights with a small interest in numbers. But, life isn't all about textbooks and equations for me.

Click to see my [resume](resume.docx.pdf)

Click to see my [CV](CV.pdf)

I am an international student born in Suwon, Korea. I've lived in Canada for almost a decade. For people who are not familiar where Suwon is located: this is where my hometown, Suwon is located.

```{r}
#| echo: false
#| warning: false
#| message: false
library(babynames)
library(leaflet)
library(mapdeck)
library(shiny)
library(tidyverse)
library(troopdata)
library(usethis)
library(dplyr)
library(plotly)

bases <- get_basedata()

filtered_bases <- bases %>%
  filter((countryname == "Korea, South"& basename == "Suwon AB, Suwon"))

# Now apply the encoding just in case
Encoding(filtered_bases$basename) <- "latin1"

# Use leaflet to plot only these locations
leaflet(data = filtered_bases) %>%
  addTiles() %>%
  addMarkers(
    lng = filtered_bases$lon,
    lat = filtered_bases$lat,
    popup = filtered_bases$basename,
    label = filtered_bases$countryname
  )
```

\n When I'm not deep in study, you can find me lost in a good game, strumming away on my guitar, catching the latest movies, or vibing to some great tunes. Each of these escapes offers me a different flavor of creativity and relaxation, shaping who I am outside the academic world. 

Looking ahead, I've got big plans to merge my creative side with my analytical skills by launching a marketing business in Korea. I'm drawn to Korea's vibrant culture and tech scene, and I can't wait to dive into the marketing sphere there, bringing fresh, data-driven strategies to the table.

**FUN FACT:** (not really fun)\n
The birthrate in korea has been decreasing significantly. I performed a simulation and put a visualization so that you can see how bad it is. Check out this cool interactive plot

```{r}
#| echo: false
#| warning: false
#| message: false

library(plotly)

# Adjusted hypothetical data with non-linear decline and fluctuations
years <- 2000:2020
# Create a non-linear decline with some random fluctuations
set.seed(123) # Ensure reproducibility
birth_rate <- seq(15, 6, length.out = length(years)) + rnorm(length(years), 0, 0.5)

# Create a data frame
data <- data.frame(
  Year = years,
  BirthRate = birth_rate
)

# Create an interactive plot
p <- plot_ly(data, x = ~Year, y = ~BirthRate, type = 'scatter', mode = 'lines+markers',
             line = list(color = 'blue')) %>%
  layout(title = 'Simulated Decrease in Korea\'s Birth Rate (2000-2020)',
         xaxis = list(title = 'Year'),
         yaxis = list(title = 'Birth Rate (per 1000 people)'))

# Print the plot
p

```

Thank you for visiting my website.
